A Machine Learning Approach to Kinematic Synthesis of Defect-Free Planar Four-Bar Linkages

### 2018-04-25 idetc2018_conf_version.tex
Merging into conference .tex

%%% use twocolumn and 10pt options with the asme2e format
\documentclass[twocolumn,10pt]{asme2ej}
\newcommand{\gbf}[1] {\mbox{\boldmath${#1}$\unboldmath}}
\newcommand{\R}{\hbox{I \kern -.5em R}}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{wrapfig}
\usepackage[hidelinks]{hyperref}
\usepackage{subfigure}
\usepackage{url}
\urlstyle{same}
\usepackage{caption}
\usepackage{algorithmicx}
%\usepackage{algorithm}
\usepackage{amsmath}
\usepackage[linesnumbered,ruled]{algorithm2e}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The past forty years of research in mechanism synthesis has witnessed an unprecedented volume of work in formulating and solving planar four-bar linkage synthesis problems.
However, finding practical and useful mechanisms for the motion synthesis problem has proven to be elusive as a large majority of mechanisms turn out to be defective with respect to their assembly modes.
Most methods formulate the problem as a discrete precision position problem, which inherently ignores the continuity information in the input, resulting into linkages with branch-, circuit- and order-defects.
In this paper, we bring together diverse fields of pattern recognition, machine learning, artificial neural network, and computational kinematics to present a novel approach that solves this problem both efficiently and effectively.
At the heart of this approach lies an objective function that compares the motion as a whole thereby capturing designer's intent.
In contrast to widely used structural error or loop-closure equation based error functions which convolute the optimization by considering shape, size, position and orientation simultaneously, this objective function computes motion difference in a form invariant to similarity transformations.
We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known linkages.
The query is raised in the database for nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
In spite of highly non-linear parameters space, our approach discovers a wide pool of defect free solutions very quickly.
We show that by employing proven machine learning techniques, this work could have far-reaching consequences to creating a multitude of useful and creative conceptual design solutions for mechanism synthesis problems, which go beyond planar four-bar linkages.

\textbf{keywords}: \emph{Machine Learning, Artificial Neural Network (ANN), Path Synthesis, Motion Synthesis, Planar Four-bar linkage, Type and Dimensional Synthesis, Circuit- Order-, and Branch-Defect}

@@

\section{Introduction}
Classical mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation; for an exhaustive reference see  books from such McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
Various approaches have been proposed in the literature with the aim of finding acceptable solutions for practical situations.
However, the majority of the approaches do not account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.These defects in single degree of freedom mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.

@@

In this paper, we 1) employ pattern recognition and computational shape analysis to create a similarity transforms-independent signature for the path and motion, 2) exploit the non-linear nature of relationship between the linkage parameters and the coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
When a user inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for $k$ nearest neighbors among cluster centers in the database.
The neighbor is defined as motion or path whose part has a similar signature to the input.
These $k$ neighbors, if needed, are subjected to fine tuning by local optimization to obtain set of defect-free solutions.
We define a novel objective function for defect-free motion generation problems and a novel algorithm for partial matching of motions.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect free throughout the task.
The Fig.~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.

Path synthesis methods based on Fourier analysis do take the continuity information of the coupler path into account; however most of them are defined only for closed loop curves.
Ullah and Kota\cite{ullah1997} have presented an invariant approach towards representation and synthesis of closed paths through shape optimization. They use a combination of global and local search methods by optimizing Fourier Deviant function to compute the dimensions of planar four bar linkages without any initial guesses.
Wu et al.\cite{wu2011} presented a method for open and closed path generation based on finite Fourier series. In the case of motion generation, methods that take the branching defect into consideration limit their search in the configuration space where Grashof condition holds true. To the best of our knowledge, no motion generation methods truly take the motion continuity into account.

Due to the highly nonlinear nature of the problem, most optimization based methods require a good initial condition to start. Thus, an atlas or a design library is used to provide good initial conditions.
McGarva\cite{mcgarva1994} took the earliest approach towards creating a library for coupler trajectories based on harmonic analysis.
Wandling\cite{wandling2000} has presented an atlas based approach, where coupler paths and motions are stored in terms of Fourier Transforms.
Input motion is searched for neighbors based on Euclidean distances of Fourier Transforms.
Yue et al.\cite{yue-pathgen2011} presented a similar approach of path generation using P-Type Fourier Descriptor applicable for open curves.
In their approach, a task curve is transformed into normalized Fourier coefficients and queried for the nearest neighbor search.
The best match is returned as a solution to input. Chu et al.\cite{chu2010} presented an atlas based method for synthesizing spatial four bar linkages for function generation problems where orientation data is stored in terms of Fourier descriptors.

The above methods generate data based on uniform sampling in the linkage parameter space.
Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to non-uniform sampling of trajectory space causing under-representation of possible motions.
We address this issue by employing log-normal distribution in the linkage parameter space to generate data and perform compact clustering of the data using machine learning techniques.
A hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in the lower levels.
Wandling~\cite{wandling2000} and Yu et al.~\cite{yue-pathgen2011} have built libraries with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
In contrast to this, we need to store only one curve representing all the segments in it as our representation facilitates partial matching.
No other previous methods facilitate this partial matching of open motion curve into another open or closed curve. This reduces the data requirement even further.

Rest of this paper is organized as follows. Section~\ref{sec_sign} presents the computation of motion and path signatures.
Section~\ref{sec_distanceMetric} is comprised of evaluation criterion for two signatures based on the shape similarity, which leads to a formulation of the error function for optimization.
Section~\ref{sec_SA} discusses the nature of objective function via sensitivity analysis at a singularity.
Section~\ref{sec_db_ae} presents the database generation and clustering using auto-encoders for efficient sampling and query operations.
Finally, two case studies are presented in section~\ref{sec_example} to illustrate the efficiency and efficacy of the method.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Signatures of Coupler Path and Motion}\label{sec_sign}
The focus of the paper is on a novel method for motion generation that takes a continuous task motion or path as the input and returns defect-free linkages producing similar motion or path. The objective function evaluation requires the input motion to be transformed into a specific form, which we call the signature of input motion.
This signature representation should be invariant to similarity operations, viz. reflection, rotation, translation and scaling.
Signatures for path and motion are termed as path signature and motion signature, respectively.
For calculating path signature, we use formulations developed by Cui et.al\cite{cui2009}.
For this task, our approach requires the input in terms of a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$.

Curvature $k(t)$ of the path of a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ and its integral $K(t)$ is given by,
\begin{eqnarray}
  k(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}}, \label{curvatureEq}\\
  K(t) = \int^{t}_0 |k(t)|dt \label{kInt},
\end{eqnarray}
where $\dot{x}$, $\ddot{x}(t)$ are first and second order derivative with respect to parameter $t$.
As an example, the parametric motion could be a B-spline motion as shown in Fig~\ref{bsplineFitting} or it could be a discrete set of poses, which could be represented by a continuous signal using Fourier series.
We compute the curvature of path along the direction of $t$, using Eq.~\req{curvatureEq} and the cumulative integral by Eq.~\req{kInt}.
Figure~\ref{curvatureK} shows computed curvature and its unsigned integral of the coupler path shown in Fig.~\ref{bsplineFitting}.
It can be seen that curvature is small start, increases as the curve bends along the path and drops once again as the path straightens out. It is obvious that curvature plot will reverse if the direction of parameterizations reverses, while the integral is a monotonically increasing function.

@@

Now, we re-sample the curvature at equal intervals of $K(t)$, which is equivalent to plotting $k$ vs $K$ in Fig~\ref{signature}(a).
This is done by finding the parameter values of $t$ where $K$ changes uniformly.
For practical purposes, we find an array of parameter $t$ such that $K$ increments by 0.1.
For each value of $t$ in the array, we compute $k(K)$ and $\theta(K)$ and store it as the path and motion signatures respectively. We note that there is a one-to-one mapping between $t$ and $K$.

These signatures are invariant under similarity transformations; for proof see\cite{cui2009}.
We know that curvature changes inversely to the scale of the curve, so when it is integrated along the scaled curve, the scale factor cancels itself out. Reflection operation on the motion or the path, produces flipped path signature, but motion signature remains invariant.

Figure~\ref{signature} shows path and motion signature obtained for the motion depicted in Fig.~\ref{bsplineFitting}. It is important to note that signature depends on the direction along which we compute the curvature $k(t)$ as well as re-sample $\theta(t)$.

@@

The procedure of signature calculation presented in this section is given in Algorithm ~\ref{alg_signature}.

\begin{algorithm}
    \SetKwInOut{Input}{Input}
    \SetKwInOut{Output}{Output}
    \Input{Twice Differentiable Parametric Representation of Motion $(x:x(t), y:y(t), \theta:\theta(t))$}
    \Output{signature //discretized signal in form of an array}
    $k(t)$ = ComputeCurvature$(x, y)$ using Eq.~\ref{curvatureEq} \\
    $K(t)$ = IntergrateCumulatively($k(t)$) using Eq.~\ref{kInt} \\
    motionSignature = [] \\
    pathSignature = [] \\
    \For{$i = 0 \to max(K)$}
    {
      $tmp$ = (value of $t$ corresponding to which $K$ has value $i$) \\
      $i = i + 0.1$ \\
      motionSignature.push($k$($tmp$)) \\
      pathSignature.push($k$($tmp$))
    }
    \Return{PathSignature, MotionSignature}
    \caption{Calculate Invariant Signatures}
    \label{alg_signature}
\end{algorithm}

\section{Signature Matching and Error Function}\label{sec_distanceMetric}
The signatures obtained in the previous steps contain important information about shape of the trajectory.
In this section, we formulate functions that evaluate the similarity (or, distance) between two trajectories based on their signatures.
These distance functions can be used as error metric, which can be minimized using optimization methods.

\subsection{Partial Matching of Path Signatures}\label{sec_ncc}
When a path query is raised, it can be very useful to know whether this path already exists as a part in some other path present in the database.
This subsection presents a method for determining this partial similarity.

Let us consider two coupler paths; namely part and whole as shown in~\ref{wholePart}.
Let $p$ be path signature of the part path which acts as a template, while $W$ is path signature of the whole path that can completely embed the template as shown in Fig.~\ref{pathSignature}. The orientation information shown in Fig.~\ref{wholePart} is ignored for path matching. It will be used later for matching of motion signature.
The partial matching works as follows:

\begin{enumerate}
  \item $p$ and $W$ are expressed in terms of arrays and $W$ must contain more points than $p$.
  \item The template $p$ is slid with offset index $j$ along $W$.
  \item For each offset $j$, we compute normalized cross-correlation function given by,
\end{enumerate}
\vspace{-0.6cm}
\begin{equation}\label{nccEq}
  Cn(j, p, W) = |\sum_{i}^{p_{span}} \frac{(W(i+j) - \bar{W}(j\to j + p_{span}))(p(i) - \bar{p})}{\sqrt{\sum_{i}^{p_{span}}{(W(i+j) - \bar{W}_{p_{span}})}^2\sum_{i}^{p_{span}}{(p(i) - \bar{p})}^2}} |,
\end{equation}
where $Cn(j, p, W)$ is the normalized cross-correlation value when template $p$ is matched against $W$ at $j^{th}$ index; $p_{span}$ is the length of the array $p$ and $\bar{W}(j\to j + p_{span})$ is the mean for the values of array $W$ between index range of ($j, j+p_{span}$).

Here, $p$ acts as a template that tries to find best match against $W$ while sliding over it along $j$.
Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment.

Maximum score of the matching $Cn_{max}(p, W)$ represents similarity of the template in $W$, and offset index $j$ at which maximum occurs is the start point for matching.
As the signature reverses with reversal of the direction of sampling, we compute the correlation first in one direction and again after reversing $p$ and select the best matching score, offset index and the matching direction of sampling.
Figure~\ref{ncc} depicts normalized cross correlation function over the sliding domain $j$ for part and whole curves.

@@

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_path_signatures.eps}
  \caption{Path Signatures of part $p$ and whole $W$ from Fig.~\ref{wholePart}. The array index $i$ corresponds to the index location for the array of the $K$. The domain of path signature is scale invariant but the range still has a scaling factor, which is taken care of by normalized cross-correlation.}
\label{pathSignature}
\end{figure}

@@

\subsection{Partial Matching of Motion Signatures}\label{sec_mcc}
This section presents how a template motion can be checked against other motion for potential matching.
Consider part and whole motions shown in Fig.~\ref{wholePart}.
Let $p$ and $W$ be the motion signatures of part and whole motions, respectively as shown in Fig.~\ref{motionSignature}.
Similar to the partial matching of path signature, the cross-correlation function is given by,

\begin{equation}\label{mccEq}
  E(j, p, W) = \sum_{i}^{p_{span}} {((W(i+j) - \bar{W}(j\to j + p_{span})) - (p(i) - \bar{p}))}^2,
\end{equation}
where $E(j, p, W)$ is the dissimilarity value when template $p$ is matched to $W$ at $j^{th}$ index. Here $p$ tries to find best match against $W(i)$ while sliding over it.
Similar to path signature, motion signature is dependent on the sampling direction along the motion. Thus, we compute the dissimilarity for both direction and choose whichever is the least i.e. $E_{min}(p, W)$.
Figure~\ref{mcc} depicts dissimilarity function over the sliding domain $j$.
In this case, as shown in Fig.~\ref{mcc}, we find that the first point itself is a point where the perfect match occurs, which is consistent with the fact that we have essentially sliced the whole motion to obtain the part motion.

@@

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_mcc.eps}
  \caption{Dissimilarity function of two motion signatures along both directions. It can be seen that exact match is found at $j=0$, where template is fully embedded inside the other motion.}
\label{mcc}
\end{figure}

\subsection{Objective Function for Synthesis}
The functions in Eq.~\req{nccEq} and ~\req{mccEq} presented in the sections \ref{sec_ncc}, \ref{sec_mcc} can be used as the error measure for path and motion synthesis of any planar linkage, where the objective is to find a linkage that produces a motion whose part or whole corresponds to target motion (or path).
Thus we can formulate the path synthesis problem as,

@@

\begin{figure}
\centering
\includegraphics[width=270pt]{figure/fig_fourbar.eps}
  \caption{Parametric representation of four-bar linkage with all revolute joints. We set $l_0 = 1$ and one fixed joint at origin of the global frame along with making fixed length of the four bar parallel to x axis.}
\label{fourbar}
\end{figure}

Objective function evaluation step consists of calculation of coupler motion or path and finding its dissimilarity score.
It is important to note that representation obtained in Section~\ref{sec_sign} reduces size of the linkage parameters in optimization.
This optimization problem can be solved using search methods which do not require gradient computation.
We can employ global optimization methods such as differential evolution at the start and local optimization methods link Powell's method towards the end for faster convergence\cite{ullah1997}.
%Section~\ref{examples} presents results for the optimization technique used.

@@

\section{Sensitivity Analysis of Signatures}\label{sec_SA}
Due to the complex relationship between parameter space and generated motion, small changes in linkage parameters can produce large and discontinuous structural changes in the generated motions.
For example, a small change in crank length ($l_1$) can open a previously close coupler path.
Most of the methods based on Fourier descriptors can not capture the continuity at such singular locations, which adversely affect the optimization process.
In contrast to this behavior, the signatures derived in Sec.~\ref{sec_sign} have smooth transition at these singular locations due to shape similarity between a closed and just opened curve or motion.

>>>>

%%% use twocolumn and 10pt options with the asme2e format
\documentclass[twocolumn,10pt]{asme2e}
\newcommand{\gbf}[1] {\mbox{\boldmath${#1}$\unboldmath}}
\newcommand{\R}{\hbox{I \kern -.5em R}}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{wrapfig}
\usepackage[hidelinks]{hyperref}
\usepackage{subfigure}
\usepackage{url}
\urlstyle{same}
\usepackage{caption}
\usepackage{algorithmicx}
%\usepackage{algorithm}
\usepackage{amsmath}
\usepackage[linesnumbered,ruled]{algorithm2e}

@@

%%% Replace here with information related to your conference
\confshortname{IDETC/CIE 2018}
\conffullname{the ASME 2018 International Design Engineering Technical Conferences \&\\
              Computers and Information in Engineering Conference}

%%%%% for date in a single month, use
\confdate{26-29}
\confmonth{August}
%%%%% for date across two months, use
\confyear{2018}
\confcity{Quebec City}
\confcountry{Canada}

%%% Replace DETC2009/MESA-12345 with the number supplied to you
%%% by ASME for your paper.
\papernum{DRAFT: DETC2018-85578}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The past forty years of research in mechanism synthesis has witnessed an unprecedented volume of work in formulating and solving planar four-bar linkage synthesis problems.
However, finding practical and useful mechanisms for the motion synthesis problem has proven to be elusive, as a large majority of mechanisms turn out to be defective with respect to their assembly modes.
Most methods formulate the problem as a discrete precision position problem, which inherently ignores the continuity information in the input, resulting in linkages with branch-, circuit- and order-defects.
In this paper, we bring together diverse fields of pattern recognition, machine learning, artificial neural network, and computational kinematics to present a novel approach that solves this problem both efficiently and effectively.
At the heart of this approach lies an objective function that compares the motion as a whole thereby capturing designer's intent.
In contrast to widely used structural error or loop-closure equation based error functions which convolute the optimization by considering shape, size, position, and orientation simultaneously, this objective function computes motion difference in a form, which is invariant to similarity transformations.
We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known linkages.
The query is raised in the database for nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
In spite of highly non-linear parameters space, our approach discovers a wide pool of defect-free solutions very quickly.
We show that by employing proven machine learning techniques, this work could have far-reaching consequences to creating a multitude of useful and creative conceptual design solutions for mechanism synthesis problems, which go beyond planar four-bar linkages.

\textbf{keywords}: \emph{Machine Learning, Artificial Neural Network (ANN), Path Synthesis, Motion Synthesis, Planar Four-bar linkage, Circuit- Order-, and Branch-Defect}

@@

\section{Introduction}
Classical mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation; for an exhaustive reference, see books from McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
Various approaches have been proposed in the literature with aim of finding acceptable solutions for practical situations.
However, the majority of the approaches do not account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.
These defects in the single degree of freedom mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.

@@

In this paper, we 1) employ pattern recognition and computational shape analysis, to create a similarity transforms-independent signature for coupler path and motion, 2) exploit the non-linear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
When a user inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for $k$ nearest neighbors among cluster centers in the database.
These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
We define a novel objective function for defect-free motion generation problems and present an algorithm for partial matching of motions.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect-free throughout the task.
The Fig.~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.

Path synthesis methods based on Fourier analysis do take continuity information of the coupler path into account, however, most of them are defined only for closed loop curves.
Ullah and Kota\cite{ullah1997} have presented an invariant approach towards representation and synthesis of closed loop paths through shape optimization.
They use a combination of global and local search methods for optimizing Fourier Deviant function, to compute the dimensions of planar four-bar linkages without an initial guess.
Wu et al.\cite{wu2011} presented a method for open and closed path generation based on finite Fourier series.
In the case of motion generation, Li et al.\cite{li2016} have developed a Fourier descriptor-based approach for approximate motion generation.

Due to highly nonlinear nature of the problem, most optimization based methods require a good initial condition to start.
Thus, an atlas or a design library is used to provide good initial conditions.
McGarva\cite{mcgarva1994} took the earliest approach towards creating a library for coupler trajectories based on a harmonic analysis.
Wandling\cite{wandling2000} has presented an atlas-based approach, where coupler paths and motions are stored in terms of Fourier Transforms.
Input motion is searched for neighbors based on Euclidean distances of Fourier Transforms.
Yue et al.\cite{yue-pathgen2011} presented a similar approach of path generation using P-Type Fourier Descriptor applicable for open curves.
In their approach, a task curve is transformed into normalized Fourier coefficients and queried for the nearest neighbor search.
The best match is returned as the solution to input.
Chu et al.\cite{chu2010} presented an atlas-based method for synthesizing spatial four-bar linkages for function generation problems, where orientation data is stored in terms of Fourier descriptors.

The above methods generate data based on uniform sampling in the linkage parameter space.
Given highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to a non-uniform sampling of trajectory space causing under-representation of possible motions.
We address this issue by employing log-normal distribution in the linkage parameter space to generate data and perform compact clustering of the data using machine learning techniques.
Hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in lower levels.
Wandling~\cite{wandling2000} and Yu et al.~\cite{yue-pathgen2011} have built libraries with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
In contrast to this, we need to store only one curve representing all the segments in it as our representation facilitates partial matching.
None of the other previous methods facilitate this partial matching of open motion curve into another open or closed curve, which significantly contributes to providing a large number of solutions, and reduces the data requirement even further.

Rest of this paper is organized as follows. Section~\ref{sec_sign} presents the computation of motion and path signatures.
Section~\ref{sec_distanceMetric} is comprised of evaluation criterion for signatures based on the shape similarity, which leads to the formulation of error function for optimization.
Section~\ref{sec_SA} discusses the nature of objective function via sensitivity analysis at a singularity.
Section~\ref{sec_db_ae} presents the database generation and clustering using auto-encoders for efficient sampling and query operations.
Finally, two case studies are presented in section~\ref{sec_example} to illustrate the efficiency and efficacy of the method.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Signatures of Coupler Path and Motion}\label{sec_sign}
Focus of the paper is on a novel method for motion generation that takes a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ or path $(x:x(t), y:y(t))$ as the input and returns defect-free linkages producing similar motion or path.
The input is transformed into a representation, termed as a signature, which is invariant to similarity operations, viz. reflection, rotation, translation, and scaling.
Signatures for path and motion are termed as path signature and motion signature, respectively.
For calculating path signature, we use formulations developed by Cui et.al\cite{cui2009}.

Consider a motion given in parametric form as, $x:x(t), y:y(t), \theta:\theta(t)$.
Here, $\theta(t)$ represents the change in orientation along the path, measured with respect to initial orientation and is not restricted in the domain $[-\pi, \pi]$.

Curvature $\kappa(t)$ of the path $(x:x(t), y:y(t))$ and its integral $K(t)$ is given by,
\begin{eqnarray}
  \kappa(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}}, \label{curvatureEq}\\
  K(t) = \int^{t}_0 |\kappa(t)|dt \label{kInt},
\end{eqnarray}
where $\dot{x}(t)$, $\ddot{x}(t)$ are first and second order derivative with respect to parameter $t$.
As an example, the parametric motion could be a B-spline motion as shown in Fig~\ref{bsplineFitting}.
We compute $\kappa(t)$ and $K(t)$ along the direction of $t$, using Eq.~\req{curvatureEq} and Eq.~\req{kInt} respectively.
Figure~\ref{curvatureK} shows computed curvature and its unsigned integral of the coupler path shown in Fig.~\ref{bsplineFitting}.
It can be seen that curvature is small at the start, increases as the curve bends along the path and drops once again as the path straightens out. It is obvious that curvature plot will reverse if the direction of parameterizations reverses, while the integral is a monotonically increasing function.

@@

Now, we re-sample the curvature at equal intervals of $K(t)$, which is equivalent to plotting $\kappa$ vs $K$ in Fig~\ref{signature}(a).
This is done by finding the parameter values of $t$ where $K$ changes uniformly.
For practical purposes, we find an array of the parameter $t$ such that $K$ increments by 0.1.
For each value of $t$ in that array, we compute $\kappa(K)$ and $\theta(K)$ and store it as the path and motion signatures respectively.
We note that there is a one-to-one mapping between $t$ and $K$.

These signatures are invariant under similarity transformations; for proof see\cite{cui2009}.
We know that curvature changes inversely to scale of the curve, so when it is integrated along the scaled curve, the scale factor cancels itself out. Reflection operation produces flipped path signature, but motion signature remains invariant.
Figure~\ref{signature} shows path and motion signature obtained for the motion depicted in Fig.~\ref{bsplineFitting}. It is important to note, that the signature depends on the direction of parameter t, as shown in Fig~\ref{bsplineFitting}.
The procedure of signature calculation presented in this section is given in Algorithm ~\ref{alg_signature}.

@@

\begin{algorithm}
    \SetKwInOut{Input}{Input}
    \SetKwInOut{Output}{Output}
    \Input{Twice Differentiable Parametric Representation of Motion $(x:x(t), y:y(t), \theta:\theta(t))$}
    \Output{signature //discretized signal in form of an array}
    $\kappa(t)$ = ComputeCurvature$(x, y)$ using Eq.~\ref{curvatureEq} \\
    $K(t)$ = IntergrateCumulatively($\kappa(t)$) using Eq.~\ref{kInt} \\
    motionSignature = [] \\
    pathSignature = [] \\
    \For{$i = 0 \to max(K)$}
    {
      $tmp$ = (value of $t$ corresponding to which $K$ has value $i$) \\
      $i = i + 0.1$ \\
      motionSignature.push($\kappa$($tmp$)) \\
      pathSignature.push($\kappa$($tmp$))
    }
    \Return{PathSignature, MotionSignature}
    \caption{Calculate Invariant Signatures}
    \label{alg_signature}
\end{algorithm}

\section{Signature Matching and Error Function}\label{sec_distanceMetric}
The signatures obtained in previous steps contain important information about the shape of the trajectory.
In this section, we formulate functions that evaluate the similarity between two trajectories based on their signatures.
These distance functions can be used as error metric, which can be minimized using optimization methods.

\subsection{Partial Matching of Path Signatures}\label{sec_ncc}
When a path query is raised, it can be very useful to know whether this path matches with the part of a path from the database.
This subsection presents a method for determining this partial similarity.

Let us consider two coupler paths; namely \emph{Part} and \emph{Whole} as shown in~\ref{wholePart}.
Let $p$ and $W$ be their signatures respectively, where $W$ completely contains $p$ as shown in Fig.~\ref{pathSignature}.
The orientation information shown in Fig.~\ref{wholePart} is ignored for path matching. It will be used later for matching of motion signatures.
The partial matching works as follows:

\begin{enumerate}
  \item $p$ and $W$ are expressed in terms of arrays and $W$ must contain more points than $p$.
  \item $p$ is slid with offset index $j$ along $W$.
  \item For each offset $j$, we compute normalized cross-correlation\cite{lewis1995fast} function given by,
\end{enumerate}
\vspace{-0.6cm}
\begin{equation}\label{nccEq}
  Cn(j, p, W) = |\sum_{i}^{p_{span}} \frac{(W(i+j) - \bar{W}(j : j + p_{span}))(p(i) - \bar{p})}{\sqrt{\sum_{i}^{p_{span}}{(W(i+j) - \bar{W}_{p_{span}})}^2\sum_{i}^{p_{span}}{(p(i) - \bar{p})}^2}} |,
\end{equation}
where $Cn(j, p, W)$ is the normalized cross-correlation value when $p$ is matched against $W$ at $j^{th}$ index; $p_{span}$ is length of the array $p$ and $\bar{W}(j:j + p_{span})$ is mean of the values of array $W$ between index range of ($j, j+p_{span}$).

Here, $p$ acts as a template that tries to find the best match against $W$ while sliding over it along $j$.
Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment of $p$ inside $W$.

The maximum score of the matching $Cn_{max}(p, W)$ represents similarity of the template in $W$, and offset index $j$ at which maximum occurs is the start point for matching.
As we know that the signature reverses with reversal of the direction of $t$, we compute the correlation along both directions and select the best matching score, offset index and the matching direction of sampling.
Figure~\ref{ncc} depicts normalized cross correlation function over the sliding domain $j$ for \emph{Part} and \emph{Whole} curves.

@@

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_path_signatures.eps}
  \caption{Path Signatures of part $p$ and whole $W$ from Fig.~\ref{wholePart}. The array index $i$ corresponds to the index location for the array of the $K$. The domain of path signature is scale-invariant but the range still has a scaling factor, which is taken care of by normalized cross-correlation.}
\label{pathSignature}
\end{figure}

@@

\subsection{Partial Matching of Motion Signatures}\label{sec_mcc}
This section presents how a template motion can be checked against other motion for potential matching.
Consider \emph{Part} and \emph{Whole} motions shown in Fig.~\ref{wholePart}.
Let $p$ and $W$ be the motion signatures of the \emph{Part} and \emph{Whole} motions, respectively as shown in Fig.~\ref{motionSignature}.
Similar to partial matching of path signatures, the cross-correlation function is given by,

\begin{equation}\label{mccEq}
  E(j, p, W) = \sum_{i}^{p_{span}} {((W(i+j) - \bar{W}(j: j + p_{span})) - (p(i) - \bar{p}))}^2,
\end{equation}
where $E(j, p, W)$ is the dissimilarity value when template $p$ is matched to $W$ at $j^{th}$ index. Here $p$ tries to find the best match against $W(i)$ while sliding over it.
Similar to path signature, motion signature is dependent on the direction of $t$. Thus, we compute the dissimilarity for both directions and choose whichever is the least i.e. $E_{min}(p, W)$.
Figure~\ref{mcc} depicts dissimilarity function over the sliding domain $j$.
In this case, as shown in Fig.~\ref{mcc}, we find that the first point is the matching point, which is consistent with the fact that we have essentially sliced the whole motion to obtain the part motion.

@@

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_mcc.eps}
  \caption{Dissimilarity function of two motion signatures along both directions. It can be seen that exact match is found at $j=0$, where the template is fully embedded inside the other motion.}
\label{mcc}
\end{figure}

\subsection{Objective Function for Synthesis}
The functions in Eq.~\req{nccEq} and ~\req{mccEq} presented in the sections \ref{sec_ncc}, \ref{sec_mcc} can be used as the error measure for path and motion synthesis of any planar linkage, where the objective is to find a linkage that produces a motion whose part or whole corresponds to the target motion (or path).
Thus we can formulate the path synthesis problem as,

@@

\begin{figure}
\centering
\includegraphics[width=270pt]{figure/fig_fourbar.eps}
  \caption{Parametric representation of four-bar linkage with all revolute joints. We set $l_0 = 1$ and one fixed joint at the origin of the global frame along with making the fixed length of four-bar parallel to the x-axis.}
\label{fourbar}
\end{figure}

Objective function evaluation step consists of calculation of coupler motion or path and finding its dissimilarity score.
It is important to note that representation obtained in Section~\ref{sec_sign} reduces the size of the linkage parameters in optimization.
This optimization problem can be solved using search methods which do not require gradient computation.
We can employ global optimization methods such as differential evolution at the start, and local optimization methods link Powell's method towards the end for faster convergence\cite{ullah1997}.
%Section~\ref{examples} presents results for the optimization technique used.

@@

\section{Sensitivity Analysis of Signatures}\label{sec_SA}
Due to the complex relationship between parameter space and generated motion, small changes in linkage parameters can produce large and discontinuous structural changes in the generated motions.
For example, a small change in crank length ($l_1$) can open a previously closed coupler path.
Most of the methods based on Fourier descriptors cannot capture the continuity at such singular locations, which adversely affect the optimization process.
In contrast to this behavior, the signatures derived in Sec.~\ref{sec_sign} have a smooth transition at these singular locations due to shape similarity between closed and just opened curve or motion.
